Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-06-27 paper1.tex
copy and paste from thesis

\newcommand{\editorial}[1]{\textcolor{red}{#1}}
\DeclareRobustCommand{\ion}[2]{%
\relax\ifmmode
\ifx\testbx\f@series
{\mathbf{#1\,\mathsc{#2}}}\else
{\mathrm{#1\,\mathsc{#2}}}\fi
\else\textup{#1\,{\mdseries\textsc{#2}}}%
\fi}
\newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
\newcommand{\rottext}[2]{\multirow{#1}{*}{\rotatebox[origin=c]{90}{#2}}}

@@

The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs. Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field). Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.

@@

\begin{figure*} 
	\includegraphics[width=0.9\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss} 
\end{figure*}

@@

We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}. Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}. Finally we summarize our findings in Section \ref{sec:summary}. A follow-up to this work \citep{Boada2016a} will investigate how the techniques developed here will work in practice.

@@

% \begin{figure}
% 	\includegraphics[width=\columnwidth]{figures/hmf.pdf}
% 	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$}
% 	\label{fig: hmf}
% \end{figure}

@@

\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{ii}] line flux signal-to-noise of five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies in that bin. In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS. For these objects, we assign them zero [\ion{O}{ii}] flux, but this has no impact on our analysis. For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{ii}] flux.

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$). The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $P($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg1999}.

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} \label{fig: ifu layout} 
\end{figure}

@@

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.

@@

\section{Recovery of Parameters}\label{sec:recovery}
In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015, Boada2016a}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.

@@

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
P(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_{1D}$. In simple tests where the values of both $\sigma_{1D}$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
	\caption{Illustration of the probability based cluster mass prediction method. \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass. The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$. \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies. See text for a complete description.} \label{fig: probability corner} 
\end{figure*}

@@

\section{RESULTS}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey. Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed. Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.  We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods. We also compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.

\subsection{Recovery of Cluster Members}
\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies. We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered. The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass. We find a significant decrease in the recovery of galaxies with increasing redshift. This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts. The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.} \label{fig: recovery} 
\end{figure*}

@@

The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey. For Perfect observations, we would detect all members across all cluster masses and redshifts. Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations. But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift. So follow-up observations should be tailored to the specific science goal.

\subsection{Mass estimates}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation, in both panels, between $M_{200c}$ and $M_{pred}$. The orange, dash-dotted line is the median predicted mass for perfect observations. The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison} 
\end{figure*}

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The orange, dash-dotted line is the median predicted mass for perfect observations. The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison} 
\end{figure*}

@@

\begin{table*}
\centering
\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
		&& \multic{6}{Perfect Observations} \\
		\hline
		\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
		\hline 
		\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
		\hline
		\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
		&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
		&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
		\hline

@@

We select 4,806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies. We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits. After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.

>>>>

\newcommand{\editorial}[1]{\textcolor{red}{#1}}
\newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
\newcommand{\rottext}[2]{\multirow{#1}{*}{\rotatebox[origin=c]{90}{#2}}}

@@

The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs. Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field). Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million \hbox{[\ion{O}{II}]} emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption[Illustration of the probability based \hbox{[\ion{O}{II}]} flux prediction method.]{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log \hbox{[\ion{O}{II}]} luminosity for the SDSS galaxies located in the two highlighted regions on the right. The \hbox{[\ion{O}{II}]} luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.}
	\label{fig: oii sdss} 
\end{figure*}

@@

We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}. Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}. Finally we summarize our findings in Section \ref{sec:summary}. A follow-up to this work Boada \etal\ (in Preparation) will investigate how the techniques developed here will work in practice.

@@

% \begin{figure}
% 	\includegraphics[width=\textwidth]{figures1/hmf.pdf}
% 	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$}
% 	\label{fig: hmf}
% \end{figure}

@@

\subsection{Conditional [\ion{O}{II}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign \hbox{[\ion{O}{II}]} emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured \hbox{[\ion{O}{II}]} line flux signal-to-noise of five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.

To assign an [\ion{O}{II}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{II}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin. In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS. For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis. For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{II}] flux.

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$). The right panel shows the Log [\ion{O}{II}] luminosity distribution functions, $P($[\ion{O}{II}]$| M_r, g-r)$, which we use to assign [\ion{O}{II}] luminosity to each object. The luminosity is then converted into an [\ion{O}{II}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg1999}.

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption[HETDEX pointing strategy.]{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation. Inside each IFU HETDEX will achieve near complete coverage through three dithers. See the text for more details.} 
	\label{fig: ifu layout} 
\end{figure}

@@

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.

@@

\section{Recovery of Parameters}\label{sec:recovery}
In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{http://astlib.sourceforge.net}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
\end{equation}
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.

@@

We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
P(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
\end{equation}
where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{http://dan.iel.fm/emcee/current/}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_{1D}$. In simple tests where the values of both $\sigma_{1D}$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data (\eg, Boada \etal\ in Preparation).

@@

\begin{figure*}
		\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
	\caption[Illustration of the probability based cluster mass prediction method.]{Illustration of the probability based cluster mass prediction method. \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass. The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$. \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies. See text for a complete description.}
	\label{fig: probability corner} 
\end{figure*}

@@

\section{Results}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey. Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed. Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.  We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods. We also compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.

\subsection{Recovery of Cluster Members}
\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
	\caption[Recovery fractions for the Targeted and Survey observations.]{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies. We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered. The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass. We find a significant decrease in the recovery of galaxies with increasing redshift. This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts. The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.}
	\label{fig: recovery} 
\end{figure*}

@@

The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and \hbox{[\ion{O}{II}]} line-flux limit of the survey. For Perfect observations, we would detect all members across all cluster masses and redshifts. Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations. But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift. So follow-up observations should be tailored to the specific science goal.

\subsection{Mass estimates}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
	\caption[Probability based cluster mass predictions.]{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation, in both panels, between $M_{200c}$ and $M_{pred}$. The orange, dash-dotted line is the median predicted mass for perfect observations. The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.}
	\label{fig:Probability comparison} 
\end{figure*}

@@

\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
	\caption[ML based cluster mass predictions]{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass. The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The solid black line shows the 1:1 relation. The orange, dash-dotted line is the median predicted mass for perfect observations. The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations. The shaded regions represent the 68\% scatter around the median values.}
	\label{fig: ML comparison} 
\end{figure*}

@@

\begin{table*}
\centering
\caption[Mean bias for different bins of predicted cluster mass.]{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
&& \multic{6}{Perfect Observations} \\
\hline
\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
\hline 
\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
\hline
\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
\hline

@@

We select 4,806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies. We begin by assigning each galaxy an \hbox{[\ion{O}{II}]} flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits. After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
	\caption[ML based cluster mass predictions in the Millennium Simulation]{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line). The shaded areas show the 68\% scatter around the median. The solid black line shows the 1:1 relation. \emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass. The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison} 
\end{figure}
